---
title: "LinearModel"
author: "SaraWhitaker"
date: "12/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE) 
require(tidyverse)
require(tigerstats)
```

## Introduction

Form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

## SIMS~ARM 

```{r}
plot(SIMS~ARM,data=data)
```

This scatter plot shows that the greater the the pounds of arm force(ARM), the greater simulation(SIMS)


```{r}
cor(SIMS~ARM,data=data)
```

This number represents the correlation between sims and arm force.Correlation is a measure of the linear association between the two variables. 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The equation is SIMS = -.4.095160 + 0.054563 * ARM

```{r}
newData= data.frame(GRIP=94,ARM=88)
predict.lm(model.1,newData,interval="prediction")
```



##SIMS~GRIP
```{r}
plot(SIMS~GRIP,data=data)
```

This is a generic scatters plot of SIMS vs ARM
```{r}
cor(SIMS~GRIP,data=data)
```
the greater the pounds of the GRIP force(GRIP), the greater the simulation(SIMS)
```{r}
model.2 <-lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
The equation is -4.089675 + 0.045463 *GRIP
```{r}
basicNN <-ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

This scatter plot shows the blue line as an indicator of which is a best linear fit t predict what an average sim response would be for any grip strength.

It also shows all of the data points of each individual score and corresponding grip strength.

model(SIMS~ARM) has slighty lighter Residual standard error score of 1.226 while model2(SIMS~GRIP) is scored at 1.295

model1(SIMS~ARM) has a higher adjusted r squared score of 0.467 while model2(SIMS~GRIP)scored lower at 0.4053

models appears to be the better model because it has a lower Residual standard error score than model1 and also has a higher adjusted r square score than model2

## SIMS~ARM+GRIP


```{r}
model.3 <- lm(SIMS~ARM + GRIP ,data=data)
summary.lm(model.3)
``` 
model3 appears to be the better model because the adjusted R squared score is more than model1 or model2, and also scored lower in the Residual standard error than model 1 or 2.

## prediction 

```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.3,newData,interval="prediction")
```
fit is he predicted SIMS score when you have GRIP strength of 94 and an ARM strength of 88.

the lwr and upr are the 95% confidence intervals for predicted SIMS score when the GRIP score is 94 and ARM strength of 88.

## inferential test 

This is the inferential test to compare models.

The test is anova 

$H_0$: There is no difference in how well each model fit the data between models (model2,model3)
$H_A$:There is a difference in how well each models fits the data between models (model2,model3)

```{r}
anova(model.2,model.3)
```
## Conclusion

The P-value is 0.000000001495 which is very low.

We reject th null hypothesis because the p value is too low; there is a difference between model2 and model3, we have evidence that model3 is better than model2.

